Supporting Information for: \\ Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-19 paper/arxiv/main_3_introduction.tex
clean up abbreviations

In this context, researchers have explored descriptor-based methods
to circumvent QM calculations and establish direct correlations
between target properties and electronic factors, commonly referred to as descriptors or features.
Traditional methods of crafting descriptors, as seen in the d-band model of Hammer and Nørskov \cite{hammer1995electronic},
necessitate meticulous selection of chemical properties based on chemical knowledge
and are inherently case-dependent \cite{kajita2017universal}.
Particularly in the case of SACs, the relationship is intricate,
rendering manual crafting inadequate \cite{han2021single, thirumalai2018investigating}.
To streamline this featurization process, we employed convolutional neural networks (CNNs),
which autonomously derive a hierarchical representation directly from the electronic density of state (eDOS)
\cite{tran2015learning, socher2012convolutional, krizhevsky2012imagenet}.
This approach accurately maps to the activity space, negating the need for manual crafting of descriptors
and providing a more efficient method to understand and
establish the structure-mechanism-activity relationship for electrochemical reactions.

>>>>

In this context, researchers have explored descriptor-based methods
to circumvent QM calculations and establish direct correlations
between target properties and electronic factors, commonly referred to as descriptors or features.
Traditional methods of crafting descriptors, as seen in the d-band model of Hammer and Nørskov \cite{hammer1995electronic},
necessitate meticulous selection of chemical properties based on chemical knowledge
and are inherently case-dependent \cite{kajita2017universal}.
Particularly in the case of SACs, the relationship is intricate,
rendering manual crafting inadequate \cite{han2021single, thirumalai2018investigating}.
To streamline this featurization process, we employed CNNs,
which autonomously derive a hierarchical representation directly from the eDOS
\cite{tran2015learning, socher2012convolutional, krizhevsky2012imagenet}.
This approach accurately maps to the activity space, negating the need for manual crafting of descriptors
and providing a more efficient method to understand and
establish the structure-mechanism-activity relationship for electrochemical reactions.

### 2024-01-19 paper/arxiv/main_4.2_volcano_plots.tex
use sentence-style capitalization
clean up abbreviations

% Figure 3: Limiting Potential Volcano Plot and Periodic Table
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig3_volcano.png}
    \caption{\textbf{Limiting Potential Volcano Plot and Periodic Table.}
    \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
    linear scaling relations at potential of -0.17 V vs SHE.
    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent
    metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
    graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
    Dotted purple lines delineate regions representing rate-determining steps (RDS),
    with roman numerals denoting the respective RDS for each region.
    The reaction steps are defined in \cref{main_eq1:co2rr1} to \cref{main_eq8:co2rr8}.
    \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
    single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
    \label{main_fig3:volcano}
\end{figure}

Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's \cite{peterson2012activity},
goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance \cite{balandin1969modern, deutschmann2000heterogeneous}.
Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor,
which encompasses both C- and O- bonding types of CO\textsubscript{2}RR intermediates within the scaling relations.
This adaptation arose from the intuition that most CO\textsubscript{2}RR intermediates are featured with both bonding types rather than any single one in dominance.
By integrating both bonding featured descriptors into the hybrid approach, we found the coefficient of determination ($R^2$) was increased by 0.1387.
Detailed information about the scaling parameters and performance enhancements are provided in Supplementary \cref{supp_table13:scaling_params} and Supplementary \cref{supp_fig10:r2_hyb_des}.
This improvement to some extent underscored our premise that CO\textsubscript{2}RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
After taking this dual nature into consideration, our hybrid-descriptor method can evaluate the intermediates adsorption energies more accurately.
Importantly, the introduction of hybrid descriptors is computationally affordable compared to DFT methods,
as it involves only a set of linear regressions to identify the optimal mixing ratio, as elaborated in the Methods section.

>>>>

% Figure 3: Limiting Potential Volcano Plot and Periodic Table
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig3_volcano.png}
    \caption{\textbf{Limiting potential volcano plot and periodic table.}
    \textbf{a}. Limiting potential volcano plot computed from hybrid-descriptor-based
    linear scaling relations at potential of -0.17 V vs SHE.
    In the plot, the circle, triangle, square, diamond, plus, and star symbols represent
    metals supported on g-C\textsubscript{3}N\textsubscript{4}, nitrogen-doped graphene,
    graphene with dual-vacancy, black phosphorous, BN, and C\textsubscript{2}N, respectively.
    Dotted purple lines delineate regions representing rate-determining steps,
    with roman numerals denoting the respective RDS for each region.
    The reaction steps are defined in \cref{main_eq1:co2rr1} to \cref{main_eq8:co2rr8}.
    \textbf{b}. Limiting potential periodic table illustrating the theoretical activity of
    single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.}
    \label{main_fig3:volcano}
\end{figure}

Catalyst activity volcano plots, built upon the scaling relations proposed by Peterson and Nørskov's \cite{peterson2012activity},
goes beyond assessment of candidatures' energetics only but to provide informative guidance on discovering catalysts candidates with superior performance \cite{balandin1969modern, deutschmann2000heterogeneous}.
Our endeavor to improve the accuracy of volcano plots leads to the development of the hybrid-descriptor,
which encompasses both C- and O- bonding types of CO\textsubscript{2}RR intermediates within the scaling relations.
This adaptation arose from the intuition that most CO\textsubscript{2}RR intermediates are featured with both bonding types rather than any single one in dominance.
By integrating both bonding featured descriptors into the hybrid approach, we found the $R^2$ was increased by 0.1387.
Detailed information about the scaling parameters and performance enhancements are provided in Supplementary \cref{supp_table13:scaling_params} and Supplementary \cref{supp_fig10:r2_hyb_des}.
This improvement to some extent underscored our premise that CO\textsubscript{2}RR intermediates typically exhibit chemical similarities encompassing both O- and C-type descriptors.
After taking this dual nature into consideration, our hybrid-descriptor method can evaluate the intermediates adsorption energies more accurately.
Importantly, the introduction of hybrid descriptors is computationally affordable compared to DFT methods,
as it involves only a set of linear regressions to identify the optimal mixing ratio, as elaborated in the Methods section.
